CLT Results

### 2022-03-30 analysis/clt_irt_analysis.Rmd
add new priors

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)

@@

```{r}
data <- read_csv("../data/clt_clean_data")
```

@@

@@

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = c(prior(normal(0, 1.5), class = Intercept),
            prior(student_t(10, 0, 1), class = sd)),
  cores = 4,
  chains = 4,
  iter = 8000
)
```
### Model checks

@@

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = c(prior(normal(0, 1.5), class = b, nlpar = eta),
            prior(normal(0, 1), class = b, nlpar = logalpha),
            prior(student_t(10, 0, 1), class = sd, nlpar = eta),
            prior(student_t(10, 0, 1), class = sd, nlpar = logalpha),
            prior(lkj(2), class = cor)),
  cores = 4,
  chains = 4,
  iter = 8000
)
```

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = c(prior(normal(0, 1.5), class = b, nlpar = eta),
            prior(normal(0, 1), class = b, nlpar = logalpha),
            prior(student_t(10, 0, 1), class = sd, nlpar = eta),
            prior(student_t(10, 0, 1), class = sd, nlpar = logalpha),
            prior(lkj(2), class = cor)),
  cores = 4,
  chains = 4,
  iter = 8000
)

@@

@@

```{r}
iic3 <- posterior_samples(irt3)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  mutate(p = 0.25+0.75*(inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi))))%>%
  mutate(i = p * (1 - p)) %>% 
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)

@@

```{r}
data <- read_csv("../data/clt_clean_data.csv")

aoa <-  read_xlsx("../data/word_list.xlsx")%>%
  select(german,english, aoa_german_comb)%>%
  filter(german != "rakete")%>%
  rename(targetWord = english)%>%
  mutate(targetWord = ifelse(targetWord == "frying pan", "fryingpan", targetWord),
         targetWord = ifelse(targetWord == "courgette", "zucchini", targetWord),
         targetWord = ifelse(targetWord == "rocket", "arugula", targetWord),
         targetWord = ifelse(targetWord == "palm tree", "palmtree", targetWord))%>%
  filter(german != "kappe", 
         german != "karotte", 
         german != "mohrrübe")%>%
  distinct(german, .keep_all = T)%>%
  mutate(group = cut(aoa_german_comb, 
                   breaks=c(0, 3.5, 6, Inf), 
                   labels=c("low","middle","high")))
```

@@

```{r}
prior_1pl <- 
  prior("normal(0, 2)", class = "Intercept") +
  prior("normal(0, 3)", class = "sd", group = "subjID") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord")
```

@@

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt1, "../saves/irt1.rds")
```
### Model checks

@@

```{r}
prior_2pl <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "targetWord", nlpar = "logalpha")
```

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_2pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt2, "../saves/irt2.rds")
```

@@

```{r}
prior_3pl_fixed <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "targetWord", nlpar = "logalpha")
```

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3, "../saves/irt3.rds")

@@

```{r}

beta <- item_pars_3pl_fixed[, , "beta_Intercept"] %>%
  posterior_summary() %>%
	as_tibble() %>%
	rownames_to_column() 
# slopes
alpha <- item_pars_3pl_fixed[, , "logalpha_Intercept"] %>%
  exp() %>%
  sweep(1, person_sds_3pl_fixed, "*") %>%
  posterior_summary() %>%
	as_tibble() %>%
	rownames_to_column()
item_pars_3pl_fixed <- bind_rows(beta, alpha, .id = "nlpar") %>%
	rename(item = "rowname") %>%
	mutate(item = as.numeric(item)) %>%
	mutate(
	  nlpar = factor(nlpar, labels = c("Location", "Slope")),
	  method = "MCMC-H"  
	)

coef_irt3 <- coef(irt3)

eta <- coef_irt3$targetWord[, , "eta_Intercept"] %>%
	as_tibble(rownames = "item")

alpha <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>%
	exp() %>%
	as_tibble(rownames = "item")

ggplot(params,aes(reorder(item, -aoa_german_comb), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item")+
  theme_minimal()
```

@@

```{r}
iic3 <- posterior_samples(irt3)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  mutate(p = inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi)))%>%
  mutate(i = p * (1 - p)) %>% 
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3, "../saves/irt3.rds")
```
